Clustering Constraints on the Relative Sizes of Central and Satellite Galaxies

### 2017-11-02 paper/galsize_paper.tex
Finished draft of section 4.4

As we will show in \S\ref{sec:results}, the chief ingredient needed to recover the observed clustering properties of galaxies is that satellites need to be smaller than centrals of comparable halo mass. Thus it is natural to consider a class of models in which stellar mass is stripped from satellite galaxies after infall.

@@

\dots, in which $\rhalf$ is statistically set by present-day stellar mass with no other dependencies. Thus neither of the above features are present: satellites and centrals of the same mass have no differences in size, and there is essentially no $\rhalf-$dependence to galaxy clustering, in gross disagreement with our SDSS observations.

We conclude this section with a discussion of Figure \ref{fig:strippingorphans}, which provides an estimate of how satellite mass stripping and orphan galaxies impact size-dependent clustering ratios. In the $\mstar+$stripping model described in \S\ref{subsubsec:strippingmodel}, satellites lose stellar mass in a way that mimics what is seen in high-resolution hydrodynamical simulations. This naturally results in an enhancement of size differences between satellites and centrals, and the dot-dashed curves in Figure \ref{fig:strippingorphans} show that produces the expected sign of the effect on the clustering ratios. The magnitude of the effect, however is not strong enough to remedy the discrepancy of the clustering predictions of the $\mstar-$based model. We discuss the physical implications of this result in \S\ref{subsec:satellite_discussion}.

%---------------------------------------------------------------------------------------------------
\begin{figure}
\centering
\includegraphics[width=8cm]{FIGS/alt_model_wp_ratios.pdf}
\caption{
{\bf Impact of tidal stripping.}
In all panels, the axes and points with error bars are the same as in Figure \ref{fig:clustering_ratio_upshot}. The solid green curves shows the prediction of the $\mstar-$based model, which is in gross tension with the data due to satellites having the same size as centrals of the same mass. The solid purple curves show results for a model in which satellites lose mass after infall in a manner similar to what is seen in high-resolution hydrodynamical simulations, as described in \S\ref{subsubsec:strippingmodel}. This produces satellites that are smaller than centrals, but the effect is too mild to correctly capture the observed clustering. Evidently, satellite-specific mass stripping plays a sub-dominant role in setting the relative size of centrals and satellites.
}
\label{fig:strippingorphans}
\end{figure}
%-----------------------------------------------------------------------------------------------------

The dotted curves in Figure \ref{fig:strippingorphans} show results of the $\rvir-$based model applied to a subhalo catalog that includes a orphan halos. As described in \S\ref{}, orphan halos are subhalos that are no longer resolved by {\tt Rockstar}, but whose evolution is tracked in a post-processing phase. We apply the same mass-stripping model described in \S\ref{subsubsec:strippingmodel} to this subhalo catalog that includes orphan halos, keep all model galaxies that retain more than half of their stellar mass, and show results for the $\rvir-$based model applied to the resulting catalog.

As the orphan catalog has a higher satellite fraction than the standard subhalo catalog, the negative boost shown the dotted curves in Figure \ref{fig:strippingorphans} is expected. Orphan halos also typically have earlier-than-average values of $\zpeak$ relative to ordinary subhalos, which also enhances differences between central and satellite sizes. See \S\ref{subsec:satellite_discussion} for further discussion.

@@

@@

>>>>

As we will show in \S\ref{sec:results}, the chief ingredient needed to recover the observed clustering properties of galaxies is that satellites need to be smaller than centrals of comparable halo mass. Thus it is natural to consider a class of models in which stellar mass is stripped from satellite galaxies after infall.
 %satellites lose stellar mass in a way that mimics what is seen in high-resolution hydrodynamical simulations.

@@

The green curves in Figure~\ref{fig:mstarmodelclustering} test the clustering predictions of the $\mstar-$based model described in \S\ref{subsubsec:mstaronlymodel}. In this model, $\rhalf$ is a log-normal distribution centered at $\median{\rhalf}{\mstar}.$ By construction, this model predicts no dependence at all of galaxy clustering upon $\rhalf$ at fixed $\mstar,$ even though the observed one-point distributions are recovered exactly.

The reason for the null signal of the purely $\mstar-$based model is simply that the scatter of $\rhalf$ about $\median{\rhalf}{\mstar}$ is uncorrelated with any other property. This is in contrast to the $\rvir-$based model, which correlates the scatter with host halo mass and as well as subhalo assembly. The purely $\mstar-$based model gives us a useful starting point to test simple alternative hypotheses for how the scatter may be correlated with large-scale structure. This is the motivation behind the $\mstar+$stripping model described in \S\ref{subsubsec:strippingmodel}. In this alternative model, satellites have smaller sizes than centrals of the same $\mstar$ due to post-infall stripping, where the amount of stripping has been calibrated to the satellite mass loss seen in high-resolution hydrodynamical simulations.

The treatment of stellar mass loss in this model naturally results in an enhancement of size differences between satellites and centrals. As shown by the purple curves in Figure \ref{fig:mstarmodelclustering}, these central/satellite differences impact $\rhalf-$dependent clustering in the expected manner: small galaxies cluster more strongly relative to large galaxies of the same stellar mass. Since the satellite fraction increases with decreasing stellar mass, the clustering ratios are more negative for samples with smaller $\mstar$ thresholds. This confirms the notion that central vs. satellite differences drive the $\rhalf-$dependence of clustering, although the magnitude of the effect is evidently is not strong enough to produce clustering predictions that are consistent with SDSS. It is difficult to strip enough mass from satellites so that the $\rhalf-$dependent clustering is in agreement with observations. Taken together with the results for the $\rvir-$based model presented in \S\ref{subsec:clustering_results} and shown in Figure \ref{fig:clustering_ratio_upshot}, this supports the conclusion that the relative difference between central and satellite size is at least partially in place at the time of satellite infall. We discuss the physical implications of this result in \S\ref{subsec:satellite_discussion}.

%---------------------------------------------------------------------------------------------------
\begin{figure}
\centering
\includegraphics[width=8cm]{FIGS/alt_model_wp_ratios.pdf}
\caption{
{\bf Impact of tidal stripping.}
In all panels, the axes and points with error bars are the same as in Figure \ref{fig:clustering_ratio_upshot}. The solid green curves shows the prediction of the $\mstar-$based model, which is in gross tension with the data due to satellites having the same size as centrals of the same mass. The solid purple curves show results for a model in which satellites lose mass after infall in a manner similar to what is seen in high-resolution hydrodynamical simulations, as described in \S\ref{subsubsec:strippingmodel}. This produces satellites that are smaller than centrals, but the effect is too mild to correctly capture the observed clustering. Evidently, satellite-specific mass stripping plays a sub-dominant role in setting the relative size of centrals and satellites.
}
\label{fig:mstarmodelclustering}
\end{figure}
%-----------------------------------------------------------------------------------------------------

@@

Our treatment of satellite-specific mass loss with the $\mstar+$stripping model is only approximate, because we have  modified the size of satellites without self-consistently modifiying their total stellar mass. In the present work, we have opted not to develop and fine-tune a more complex, semi-analytic model; instead, we have made a simple estimate for the level at which satellite-specific stripping impacts the two-point function.

@@

%As the orphan catalog has a higher satellite fraction than the standard subhalo catalog, the negative boost shown the dotted curves in Figure \ref{fig:strippingorphans} is expected. Orphan halos also typically have earlier-than-average values of $\zpeak$ relative to ordinary subhalos, which also enhances differences between central and satellite sizes. See \S\ref{subsec:satellite_discussion} for further discussion.
